Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-04 RNARedPrint.tex
Author order; add proper initials

% \author[Hammer, Ponty, Wang and Will]{Stefan Hammer\,$^{\text{\sfb 1,2,3}}$, Yann Ponty\,$^{\text{\sfb 4,5,}\star}$, Wei Wang\,$^{\text{\sfb 4}}$ and Sebastian Will\,$^{\text{\sfb 2}}$}

\author[
    addressref={aff1,aff2,aff3},
    email={stefan.hammer@uni-leipzig.de}
]{\inits{F}\fnm{Stefan} \snm{Hammer}}
%
\author[
    addressref={aff4,aff5},
    corref={aff4},                       % id of corresponding address, if any
    email={yann.ponty@lix.polytechnique.fr}
]{\inits{F}\fnm{Yann} \snm{Ponty}}
%
\author[
    addressref={aff4},
    email={wei.wang@lix.polytechnique.fr}
]{\inits{F}\fnm{Wei} \snm{Wang}}
%
\author[
    addressref={aff2,aff3},
    %corref={aff2},                       % id of corresponding address, if any
    email={will@tbi.univie.ac.at}
]{\inits{S}\fnm{Sebastian} \snm{Will}}

>>>>

\author[
    addressref={aff1,aff2,aff3},
    email={stefan.hammer@uni-leipzig.de}
]{\inits{SH} \fnm{Stefan} \snm{Hammer}}
%
\author[
    addressref={aff4},
    email={wei.wang@lix.polytechnique.fr}
]{\inits{WW} \fnm{Wei} \snm{Wang}}
%
\author[
    addressref={aff2,aff3},
    email={will@tbi.univie.ac.at}
]{\inits{SW} \fnm{Sebastian} \snm{Will}}
%
\author[
    addressref={aff4,aff5},
    corref={aff4},                       % id of corresponding address, if any
    email={yann.ponty@lix.polytechnique.fr}
]{\inits{YP} \fnm{Yann} \snm{Ponty}}
